### 2012-12-14 doc/description.tex
start working on including data into model

 \inference{d \vdash cardinality(p) = 1 \\ \wedge \exists t : t = table(name(owningClass(p)), d)}{d \vdash columns(t) \cup column(name(p), \rho_t(type(p)), NOTNULL)} \\ \\

@@

>>>>

 \inference{ d \vdash cardinality(p) = 1 
 \\ \wedge \exists t : t = table(name(owningClass(p)), d) 
 \\ \wedge \not instanciated(owningClass(p))
 }{ d \vdash columns(t) \cup column(name(p), \rho_t(type(p)), NOTNULL)} \\ \\

@@

The new foreign key can cause inconsistency of the system when added to a table which contains data. This case is not handled by the mapping function above. We have to extend the function definition of a feature that allows the mapping between the data in both tables. The mapping is a function:
$$f_m : Property \rightarrow Instance \times Instance $$
